---
title: "hw6"
author: "Yiyao LI"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r load_libraries, include=FALSE}
library(tidyverse)
library(modelr)
library(p8105.datasets)
library(mgcv)
library(patchwork)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2

read in the data

```{r}
baby_df = 
  read_csv("./data/birthweight.csv")
```

clean the data for regression analysis
factors: babysex, malform, frace, mrace

```{r}
baby_df=
baby_df %>%
   mutate(
     babysex = case_when(
       babysex == 1 ~ "male", 
       babysex == 2 ~ "female"),
     malform = case_when(
       malform == 0 ~ "absent",
       malform == 1 ~ "present"),
     frace = recode(frace, `1` = "White", `2`="Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown"),
     mrace = recode(mrace, `1` = "White", `2`="Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown"))
```

regression model:

first step: select variables

```{r, include = FALSE}
select_df = 
  lm(bwt ~ ., data = baby_df) %>% 
  step(., direction='backward') %>% 
  broom::tidy()
```

```{r}
select_df
select_data = lm(
  bwt ~ bhead + blength + delwt + fincome + gaweeks + mheight + parity + ppwt + smoken + babysex + mrace, data = baby_df)
```

I found there are interesting positive relationship between delwt and bwt. Also, momheight is positively related to bwt. Here is the regression process to explore the relationships.

```{r}
baby_df %>%
  ggplot(aes(x=delwt,y=bwt,color=mheight))+
  geom_point(size=1.2, alpha=0.5) 
```

From the plot, we can infer that delwt is positively related to mheight. And delwt and mheight are both positively related to bwt.

```{r}
linear_df = lm(bwt ~ delwt + mheight, data = baby_df)
broom::tidy(linear_df)
```

The linear_df attested my assumption.

```{r}
delwt_r=
modelr::add_residuals(baby_df, linear_df) %>%
  ggplot(aes(x=delwt,y=resid,color = delwt))+
   geom_point() 

mheight_r=
modelr::add_residuals(baby_df, linear_df) %>%
  ggplot(aes(x=mheight,y=resid,color = mheight))+
   geom_point() 

residuals = delwt_r + mheight_r
residuals
```

```{r}
delwt_p=
modelr::add_predictions(baby_df, linear_df) %>%
  ggplot(aes(x=delwt,y=pred,color= delwt))+
   geom_point() 

mheight_p=
modelr::add_predictions(baby_df, linear_df) %>%
  ggplot(aes(x=mheight,y=pred,color = mheight))+
   geom_point() 

predictions = delwt_p + mheight_p
predictions
```


### comparison


```{r}
model_blength_gaweeks = lm(bwt ~ blength + gaweeks, data = baby_df)

model_mixture = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = baby_df)
```

#### Compare

```{r}
cv_df =
  crossv_mc(baby_df,100) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    model  = map(.x = train, ~lm(bwt ~ delwt + mheight, data = .x)),
    model_blength_gaweeks = map(.x = train, ~ lm(bwt ~ blength + gaweeks, data = .x)),
    model_mixture = map(.x = train, ~lm(bwt ~ bhead * blength * babysex, data = .x))) %>% 
  mutate(
    rmse_model = map2_dbl(model, test, ~rmse(model = .x, data = .y)),
    rmse_model_bg = map2_dbl(model_blength_gaweeks, test, ~rmse(model = .x, data = .y)),
    rmse_model_mix = map2_dbl(model_mixture, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```


```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>%
  group_by(model) %>%
  summarize(avg_rmse = mean(rmse))
```

Model_mixture has the smallest rmse, which means it is better for predicting birthweight.

## Problem 3

```{r, message = FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
set.seed(77)
weather_b_rsquared = 
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)), 
    results = map(models, broom::glance)
  )%>% 
  select(results) %>% 
  unnest(results) 
```

```{r}
weather_b_rsquared %>% 
  ggplot(aes(x = r.squared)) + 
  geom_histogram()
```

It follows a normal distribution distribution and the mean value is around 0.91.

```{r}
weather_b_rsquared %>%
  summarise(
    ci_lower=quantile(r.squared,0.025),
    ci_upper=quantile(r.squared,0.975)
  )
```

The confidence interval of rsquared is (0.894, 0.928).

```{r}
set.seed(77)
weather_b_log = 
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)), 
    results = map(models, broom::tidy)
  )%>% 
  select(results, strap_number) %>% 
  unnest(results)%>%
  select(term, estimate, strap_number) %>% 
  pivot_wider(
    names_from = "term",  
    values_from = "estimate") %>% 
  mutate( log = log(`(Intercept)`*tmin))
```

```{r}
weather_b_log %>% 
  ggplot(aes(x = log)) + 
  geom_histogram() 
```

It follows a normal distribution and the mean value is around 2.02.

```{r}
weather_b_log %>%
  summarise(
    ci_lower=quantile(log,0.025),
    ci_upper=quantile(log,0.975)
  )
```

The 95% confidence interval is (1.96, 2.06).

